### 2023-05-01 chapter2/chapter2_supporting.tex
Added table of selected annotations

>>>>

\clearpage  % Force display of all figures before table

\footnotesize
\begin{longtable}{|l|r|l|l|}
\caption{\textbf{Selected enriched annotations in clusters.}}
\label{stable:annotations}
\textbf{Cluster} & \multicolumn{1}{c|}{\textbf{\textit{p}-value}} & \textbf{Term ID} & \textbf{Term name}                                                    \endfirsthead
A                & 1.38E-03                                       & GO:0005201       & ~extracellular matrix structural constituent                          \\
A                & 3.38E-03                                       & GO:0043062       & ~extracellular structure organization                                 \\
A                & 9.48E-03                                       & GO:0030198       & ~extracellular matrix organization                                    \\
B                & 3.64E-04                                       & GO:0090263       & ~positive regulation of canonical Wnt signaling pathway               \\
B                & 4.32E-04                                       & GO:0060828       & ~regulation of canonical Wnt signaling pathway                        \\
B                & 5.04E-04                                       & GO:0030177       & ~positive regulation of Wnt signaling pathway                         \\
B                & 8.91E-04                                       & GO:0030111       & ~regulation of Wnt signaling pathway                                  \\
B                & 3.98E-03                                       & GO:0061629       & ~RNA polymerase II-specific DNA-binding transcription factor binding  \\
B                & 7.15E-03                                       & GO:0008134       & ~transcription factor binding                                         \\
D                & 2.44E-03                                       & GO:0006999       & ~nuclear pore organization                                            \\
D                & 3.23E-03                                       & GO:0006607       & ~NLS-bearing protein import into nucleus                              \\
D                & 3.60E-03                                       & GO:0008104       & ~protein localization                                                 \\
D                & 3.74E-03                                       & GO:0045184       & ~establishment of protein localization                                \\
D                & 3.78E-03                                       & GO:0044613       & ~nuclear pore central transport channel                               \\
D                & 3.78E-03                                       & GO:0017056       & ~structural constituent of nuclear pore                               \\
E                & 3.66E-04                                       & GO:0070161       & ~anchoring junction                                                   \\
E                & 7.11E-04                                       & GO:0030054       & ~cell junction                                                        \\
E                & 1.66E-03                                       & GO:0022843       & ~voltage-gated cation channel activity                                \\
E                & 2.12E-03                                       & GO:0022832       & ~voltage-gated channel activity                                       \\
E                & 2.12E-03                                       & GO:0005244       & ~voltage-gated ion channel activity                                   \\
F                & 2.92E-04                                       & GO:0033365       & ~protein localization to organelle                                    \\
F                & 4.08E-04                                       & GO:0051179       & ~localization                                                         \\
F                & 5.43E-04                                       & GO:0034504       & ~protein localization to nucleus                                      \\
F                & 8.68E-04                                       & GO:0034613       & ~cellular protein localization                                        \\
F                & 1.57E-03                                       & GO:0008104       & ~protein localization                                                 \\
F                & 1.67E-03                                       & GO:0006606       & ~protein import into nucleus                                          \\
F                & 2.10E-03                                       & GO:0051170       & ~import into nucleus                                                  \\
G                & 2.40E-04                                       & GO:0005459       & ~UDP-galactose transmembrane transporter activity                     \\
G                & 2.40E-04                                       & GO:0005338       & ~nucleotide-sugar transmembrane transporter activity                  \\
G                & 2.40E-04                                       & GO:0015165       & ~pyrimidine nucleotide-sugar transmembrane transporter activity       \\
G                & 2.40E-04                                       & GO:0072334       & ~UDP-galactose transmembrane transport                                \\
G                & 2.40E-04                                       & GO:0090481       & ~pyrimidine nucleotide-sugar transmembrane transport                  \\
G                & 2.40E-04                                       & GO:0015780       & ~nucleotide-sugar transmembrane transport                             \\
G                & 1.41E-03                                       & GO:0015932       & ~nucleobase-containing compound transmembrane transporter activity    \\
G                & 2.33E-03                                       & GO:1901505       & ~carbohydrate derivative transmembrane transporter activity           \\
G                & 2.33E-03                                       & GO:1901264       & ~carbohydrate derivative transport                                    \\
H                & 2.14E-04                                       & GO:0007113       & ~endomitotic cell cycle                                               \\
H                & 1.51E-03                                       & GO:0051726       & ~regulation of cell cycle                                             \\
I                & 5.02E-04                                       & GO:0007616       & ~long-term memory                                                     \\
I                & 6.03E-04                                       & GO:0099177       & ~regulation of trans-synaptic signaling                               \\
I                & 6.03E-04                                       & GO:0050804       & ~modulation of chemical synaptic transmission                         \\
I                & 8.90E-04                                       & GO:0010646       & ~regulation of cell communication                                     \\
I                & 9.41E-04                                       & GO:0023051       & ~regulation of signaling                                              \\
J                & 1.34E-03                                       & GO:0016829       & ~lyase activity                                                       \\
J                & 1.47E-03                                       & GO:0008172       & ~S-methyltransferase activity                                         \\
J                & 2.37E-03                                       & GO:0042800       & ~histone methyltransferase activity (H3-K4 specific)                  \\
J                & 3.76E-03                                       & GO:0034708       & ~methyltransferase complex                                            \\
J                & 4.79E-03                                       & GO:0051568       & ~histone H3-K4 methylation                                            \\
J                & 8.43E-03                                       & GO:0035097       & ~histone methyltransferase complex                                    \\
L                & 2.51E-03                                       & GO:0031507       & ~heterochromatin assembly                                             \\
L                & 2.51E-03                                       & GO:0031497       & ~chromatin assembly                                                   \\
L                & 3.00E-03                                       & GO:0070828       & ~heterochromatin organization                                         \\
L                & 3.91E-03                                       & GO:0003677       & ~DNA binding                                                          \\
L                & 4.70E-03                                       & GO:0003676       & ~nucleic acid binding                                                 \\
